Multidimensional analysis and detection of informative features in human brain white matter

### 2021-02-05 reports/manuscript/paper.tex
Add author's summary

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
\todo[inline]{Write author summary}

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{nested-cross-validation.pdf}
    \caption{{\bf Nested cross-validation}
        \label{fig:nested-cross-val}
        We evaluate model quality using a nested $k$-fold cross validation
        scheme. At level-0, the input data is decomposed into $k_0$ shuffled
        groups and optimal hyperparameters are found for the level-0 training
        set. To avoid overfitting, the optimal hyperparameters are themselves
        evaluated using a cross-validation scheme taking place at level-1 of
        the decomposition, where each level-0 training set is further
        decomposed into $k_1 = 3$ shuffled groups. In the classification
        case, the training and test splits are stratified by diagnosis. For
        the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
        $k_0 = 5$.
    }
\end{figure}

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Innovations in medical imaging are helping researchers understand the human
brain, and in particular the neural connections that comprise the white
matter. Mapping these connections and understanding which parts are relevant
to disease and behavior holds great promise in understanding how the brain
functions, diagnosing diseases, and creating more effective treatments. To
that end, there are now many large scale neuroimaging studies with thousands
or even tens of thousands of participants. As such, neuroimaging is on the
cusp of a transition to big data. Yet the field's conventional statistical
methods are better suited to the small-scale studies of the past. We need
machine learning methods that can accurately predict disease status and
behavior, while also providing insight into which parts of the white matter
are important for that prediction. We have therefore developed a statistical
method that automatically identifies important features of the white matter
for any given disease or behavior. Our approach relies on including our
knowledge of the anatomical grouping of the white matter fiber bundles in the
statistical model itself. We tested our method on four different datasets and
found that it competes with state-of-the-art methods and preserves
interpretability, all without the need for extensive feature engineering.

@@

\begin{figure}[t]
    \includegraphics[width=0.75\textwidth]{nested-cross-validation.pdf}
    \caption{{\bf Nested cross-validation}
        \label{fig:nested-cross-val}
        We evaluate model quality using a nested $k$-fold cross validation
        scheme. At level-0, the input data is decomposed into $k_0$ shuffled
        groups and optimal hyperparameters are found for the level-0 training
        set. To avoid overfitting, the optimal hyperparameters are themselves
        evaluated using a cross-validation scheme taking place at level-1 of
        the decomposition, where each level-0 training set is further
        decomposed into $k_1 = 3$ shuffled groups. In the classification
        case, the training and test splits are stratified by diagnosis. For
        the ALS and WH data, $k_0 = 10$, while for the HBN and Cam-CAN data,
        $k_0 = 5$.
    }
\end{figure}
